### 2025-09-18 paper/sec/introduction.tex
Progress on intro.

\figref{scigen-example-website}, adapted from \cite{zhang18}, shows how a transparent document appears to a
user.

@@

\rpnote{Need to illustrate counterfactual/generalisability}

@@

We leave implementing a full IDE authoring plugin (based on VSCode or Cursor, for example) for future work.

Our contribution is an agent-based tool which identifies text fragments which are candidates for being made
data-driven, generates the corresponding Fluid code, and then incrementally incorporates the code into a
data-driven version of the original document.

>>>>

\figref{scigen-example-website}, adapted from \cite{zhang18}, shows how a transparent document appears to a
user. \rpnote{Make important point about counterfactuals/generalisability}

@@

@@

We leave implementing a full authoring plugin for an IDE such as VSCode or Cursor for future work.
